---
#title: Geographic Range Size
#subtitle: Biogeography
#author: "`r input$student_name`"
mainfont: Linux Libertine O
header-includes:
  \usepackage{fontspec}
  \setmainfont[Ligatures={Common,TeX}, Contextuals={NoAlternate}, BoldFont={* Bold}, ItalicFont={* Italic}, Numbers={OldStyle}]{Linux Libertine O}
  \usepackage{microtype}
  \usepackage[sc]{titlesec}
---
\textsc{Biogeography: Geographic range size \hfill `r input$student_name`}

## Predictions

For `r paste(input$state, input$taxon)`, you wrote *`r input$predict_state`*

For North American `r paste(input$na_taxon)`, you wrote *`r input$predict_na`*

For California marine fishes, you wrote *`r input$predict_ca`*

***

Histogram of `r paste(input$state, input$taxon)` for geographic range size.

```{r fig.dim=c(3,2), echo=FALSE}
plots$state
```

Histogram of North American `r input$na_taxon` for geographic range size.

```{r fig.dim=c(3,2), echo=FALSE}
plots$na
```

Histogram of California Marine Fishes for geographic range size.

```{r fig.dim=c(3,2), echo=FALSE}
plots$na
```
